Ground state energy of quantum dots using the coupled cluster method

### 2018-06-07 project_2/article/article.tex
Performance comments in discussion

>>>>

    \subsection{Performance comparison}
        Somewhat surprisingly, the Hartree-Fock method outperforms the coupled
        cluster doubles when the harmonic oscillator basis is used. This
        happens for almost any configuration except the smallest system
        with $N=2$ particles. This comes from the fact that the HO basis is 
        not very good at representing the states in the system. As we have
        already stated, because the Hartree-Fock SCF iterations is a variational
        methdod, the basis is varied in order to find the minimal energy. The new
        basis states will be linear combinations of the old basis states. When
        the iterations are finished, the new transformed HF basis will then be 
        much better at representing the possible quantum configurations compared 
        with the HO basis. This effect is only apparent in system with a larger
        number of particles and/or low frequency. This is because in a system with 
        a large number of particles relative to the frequency particle-particle
        interaction will be more prominent than the harmonic oscillator potential
        the particles are subject to. I other words, the HO basis fits rather
        well.
